---
title: "Social attitudes"
date: "`r Sys.Date()`"
output: pdf_document
---

```{r packages}
library("dplyr")
library("haven")
```

```{r datasets}
bsa = 
    haven::read_spss("../inst/extdata/british-social-attitudes-2018/UKDA-8606-spss/spss/spss24/bsa2018_final_ukda.sav") %>%
    haven::as_factor() %>%
    filter(gor_id == "East Midlands")

aps =
    haven::read_spss("../inst/extdata/annual-population-survey-2019/UKDA-8632-spss/spss/spss25/apsp_jan-dec19_eul_pwta18.sav") %>%
    haven::as_factor() %>%
    filter(GOR9D == "East Midlands")
```


# British Social Attitudes 2018

We could use elements of the Blaise questionnaire, asked in the British Social Attitudes 2018 survey.
In particular there's a section on 'concerns' and an abridged version might be of interest:

Q514: `lifecon1c`--`lifecon3c` are derived from `LifeConc1A`, etc.
"Here is a list of things some people may feel concerned about.
I am going to ask you about the things you are most concerned about, you
can select up to three from the list.
Firstly, what would you say you are most concerned about at the moment?
Please read through the whole list before deciding."
CODE ONE ONLY

Code | Response
-----|----------
1.   | Your physical health
2.   | Your mental health
3.   | Your relationship with your partner or spouse
4.   | Your relationships with your family
5.   | Your relationships with friends
6.   | Your family's health and wellbeing
7.   | Your work-life balance
8.   | Your education, qualifications or training
9.   | Your work situation
10.  | Money or debt
11.  | Your housing situation
12.  | How safe you feel in your local area
13.  | Your appearance (including your weight and looks)
14.  | Your social life
15.  | Other (WRITE IN)
16.  | (SPONTANEOUS: No concerns)
98.  | (Don't know)
99.  | (Refusal)

For respondents in the East Midlands (no Derbyshire/Derby option) first concern:

```{r concerns}
bsa %>%
    count(lifecon1c) %>%
    arrange(desc(n))
```

Second concern:

```{r 2-concern}
bsa %>%
    count(lifecon2c) %>%
    arrange(desc(n))
```

'Next most' concerned:

```{r 3-concern}
bsa %>%
    count(lifecon3c) %>%
    arrange(desc(n))
```

# ONS Domains and Measures of National Well--being

Domains of well--being used by ONS are:

- Personal well--being
- Relationships
- Health
- What we do
- Where we live
- Personal finance
- The economy
- Education and skills
- Governance
- The natural environment

Source: `https://www.ons.gov.uk/peoplepopulationandcommunity/wellbeing/datasets/measuringnationalwellbeingdomainsandmeasures`

## Personal well--being

The personal well--being domain uses the following measures from the Annual Population Survey (taken from 2019 survey):

1. `SATIS` - Overall, how satisfied are you with your life nowadays? 0--10
1. `WORTH` - Overall, to what extent do you feel that the things you do in your life are worthwhile? 0--10
1. `HAPPY` - Overall, how happy did you feel yesterday? 0--10
1. `ANXIOUS` - On a scale where nought is 'not at all anxious' and 10 is 'completely anxious', overall, how anxious did you feel yesterday? 0--10

```{r personal-wellbeing}
aps %>% count(SATIS)
aps %>% count(WORTH)
aps %>% count(HAPPY)
aps %>% count(ANXIOUS)
```
